Incentivizing Exploration with Unbiased History

### 2018-10-23 3level.tex
stuff

They main idea for the 3-level policy is that it inserts the second
level as an additional ``checkpoint'' to induce more adaptivity in the
exploration. By running \ALGG in parellel, the first level ensures
that the agents explore both arms. In the second level, agents will
pull the best arm when $\mu_1 - \mu_2$ is large
($\tilde{\Omega}(1/\sqrt{T_1})$). Otherwise agents will explore both
arms more. In the third level, agents will pull the best arm unless
$\mu_1-\mu_2$ is much smaller ($\tilde{O}(1/\sqrt{T_2})$). In the
proof, we need not only the concentration argument as the 2-level
recommendation policy, but also the anti-concentration argument to
show that agents explore more in the second round if $\mu_1-\mu_2$ is
not too big.

>>>>

They main idea for the 3-level policy is that it inserts the second
level as an additional ``checkpoint'' to induce more adaptivity in the
exploration. While the first level ensures that the agents explore
both arms, the second level will continue to explore both arms only if
the rewards of the two arms are still indistinguishable (that is, when
$|\mu_1 - \mu_2| < \tilde{O}(1/\sqrt{T_1})$). In the third level,
agents will pull the best arm unless $|\mu_1-\mu_2|$ is much smaller
than $\tilde{O}(1/\sqrt{T_2})$, in which case pulling either arm will
incur small regret. The formal guarantee of the policy is the
following.

In the proof, we need not only the concentration argument as the
2-level recommendation policy, but also the anti-concentration
argument to show that agents explore more in the second round if
$\mu_1-\mu_2$ is not too big.
